---
title: "fraud card detection"
author: "vivek singh"
date: "23 April 2018"
output: html_document
---
##loading required libraries
```{r}
library(caret)
library(class)
library(e1071)
library(ROCR)
```
## calling a .csv file
```{r}
credit <- read.csv("creditcard.csv")
```
##the structure of the dataset was looked upon
```{r}
str(credit)
```
##Because the variable "Class" is of a class "integer", the factor transformation was performed: 
```{r}
credit$Class <- factor(credit$Class)
```
##dividing train data_set with 20% train and 80% test
```{r}
set.seed(200)
samp <- sample(1:nrow(credit), round(0.2*nrow(credit)))
credit <- credit[samp, ]
index <- createDataPartition(credit$Class, p = 0.75, list = F)
train <- credit[index, ]
test <- credit[-index, ]
```
##K-Nearest Neighbors, number of neighbours was set to 5 as a default
```{r}
knn1 <- knn(train = train[,-31], test = test[,-31], cl = train$Class, k = 5)
```
##confusion matrix
```{r}
confusionMatrix(knn1, test$Class, positive = "1")
##the model did not predict any cases of "fraud" (that is, "Class" = 1),
##though some actual cases of fraud were erroneously assigned to be non-fraud. 

```
## Naive Bayes
```{r}
bayes <- naiveBayes(Class~., data = train, laplace = 1)
bayes$apriori
##apriori frequencies suggest that the model is heavily inclined to assigning non-fraud values 
```
## predicted classes for a testing dataset confusionMatrix:
```{r}
pred <- predict(bayes, test)
confusionMatrix(pred, test$Class, positive = "1")
rawpred <- predict(bayes, test, type = "raw")
```
##measuring the performance
```{r}
ptest <- prediction(rawpred[,2], test$Class)
perf <- performance(ptest, "tpr", "fpr")
plot(perf, colorize = T)
performance(ptest, "auc")@y.values
```
# Conclusion::
##K-Nearest Neighbors algorithm clearly should be prioritized over Naive Bayes 
##in the extraction of the most accurate predictions in terms of whether a credit card 
##will be detected fraud or not, save for other, perhaps more effective, classifiers. 
